Rough Draft

### 2017-11-11 Article submission/roughdraft.tex
revised methods + results

    Questions analyzed were restricted to those posted in English (97\% of the full data). The time until event variable used in survival analysis is defined as the time since posting until a question receives its first answer. For questions that did not receive an answer by the download date, time until event values were defined as the time since posting to the time the data was downloaded. These questions were considered right censored, meaning that the exact answer times for these questions are higher than the recorded times (questions can still receive answers after the download date).

Survival was defined as the event that a question remains unanswered beyond a certain time, t. Estimates of survival probability were generated with the Kaplan-Meier method (cite). This method adjusts to the presence of right-censored, or unanswered questions. Estimates factor in the number of questions that have not been answered on each ordered interval of complete answer times. The estimates of survival probablity are the products of all probabilities up to that interval's time (fix this explanation). From these estimates, survival curves were constructed to examine the survival experience of questions. Mean, median and other percentiles of survival times were also generated.

Five-fold cross-validation was used for model building. The full data was split into five training and five test sets. Each training set contained 6,208 questions, and each test set contained 1,552 questions. Univariate analysis, performed on one of the training sets, was used to identify variables to include in the full Cox proportional hazards model. Predictors were entered into separate Cox models and the strength of association between those predictors and answer times were assessed. Those with partial likelihood ratio test p-values of less than 0.01 were included in the full model.

In each fold of cross-validation, the full model, with variables found to be signficant in univariate analysis, was built on one of the training sets and used to generate predicted hazard ratios on the corresponding test sets. To assess prediction performance, the predicted hazard ratios were entered into separate Cox models as the single quantitative predictor with answer times as the survival time. The resulting estimated hazard ratio, R-square statistic, partial likelihood ratio and p-value were assessed as indicators of the full model's performance (cite). Signficant statistics would indicate high predictive accuracy. Concordance statistics and Somers' Dxy were also assessed to measure the model's predictive discrimination (cite). Concordance is defined as the probability that for any two randomly chosen questions, the question with the shorter survival time also has the higher predicted hazard. Concordance statistics close to 1 indicate high discriminative ability, while statistics close to 0.5 indicate discordance, or random predictions. Somers' Dxy is the difference between the model's concordance statistic and discordance (0.5) (cite). These metrics were computed for each training and test set. The average of metrics across test sets was evaluated.

To select the final model, the model with the lowest AIC statistic and most consistent performance metrics, in that the values did not change substantially from training to test data sets, was selected.

To assess model adequacy, model residuals were examined. Martingale residuals plots were evaluated for each continuous predictor to assess the functional form. Martingale residuals are the differences between the observed number of answers received by question i, and the expected number of answers experienced by question i under the model. Deviance residuals, which are transformed martingale residuals with a mean of 0 and roughly normal distribution, were assessed to check for outliers, or questions with outcomes that are poorly predicted by the model. Score residuals, which are a measure of the approximate change in the parameter estimates that would occur if the ith question were removed from the sample, were assessed to acheck for influential questions, or questions that highly effect the parameter estimates.

After assessing model residuals, splines and other transformations were applied to variables. Restricted cubic splines were applied to continuous predictors using the method outline in \cite{Harrell2015}. As our data was fairly large (>100), splines of 5 knots were initially fit to each continuous predictor. A higher number of knots were assigned to predictors with lower p-values in the model, those thought to be more important. The optimal number of knots for each spline was determined by the model with the lowest AIC statistic. Other transformations (i.e. square root and polynomial terms) were also applied to variables.

An assumption upon which Cox regression models are built, is the assumption of porportional hazards, or that the effect of predictors on hazard doesn't depend on time. To assess this assumption, the correlations between scaled Schoenfeld resiudals and a function of time were evaluated. Schoenfeld residuals are the differences between observed and expected predictor values for each question with a complete answer time (each question that received an answer). Signficant results from this test would indicate that a predictor has violated this assumption.

@@

  Of 7,760 questions, 63.8\% received an answer by the download date. Figure a shows the distribution of answer times for all questions, grouped by whether or not the question was answered. The following statistics were calculated from Kaplan-Meier estiamtes of survival probability. The mean survival time, or the average time until a question receives its first answer is 775.75 hours, or 32.32 days. The median survival time, the time at which 50\% of the questions in the data received an answer is 9.16 hours. Table 1 provides more percentiles of survival time. Figure B shows the Kaplan-Meier curve for all questions in the data. The curve indicates that at around 100 hours after a question is posted, the probability that a question receives an answer after that time hovers around 0.35. The survival probability never reaches 0 due to the large amount of unanswered questions.

After performing univariate analysis, the predictors with partial likelihood ratio test p-values of less than 0.01 were entered into the final model. Results for univariate analysis can be seen in table 2 (results in pvalues dataframe). Each variable was entered into the Cox regression model.

The metrics for each iteration of cross validation are in table 3. Although not impressively high, the metrics did not vary substantially from test to training data, indicating that the model does not overfit.

The final model selected contained variables defined above as well as the following transformations: 
\begin{itemize}
  \item Square root of the average frequency of a question's tags. 
  \item Quadratic polynomial on the length of the question's text. 
  \item Restricted cubic spline with 5 knots on the number of characters in the device name.
  \item Restricted cubic spline with 4 knots on the average number of characters in a question's tags.
  \item Restricted cubic spline with 4 knots on the ratio of newlines to the number of characters in a question's text. 
\end{itemize}

Results for this model can be found in table z.

Assessing residuals for model adequacy indicated that assumptions were met. Score and deviance residuals showed that there were a few questions that were outliers or highly influenced the fit of the model. However, refitting the model without those questions resulted in worse predictive accuracy. Assessing the proportional hazards assumption indicated that the ``Apple Products'' level of device category was the only probable variable that violated the assumption, but as stratifying on device category substantially reduced predictive accuracy, it was left as is.

>>>>

    Questions analyzed were restricted to those posted in English (97\% of the full data). The time until event variable used in survival analysis is defined as the time since posting until a question receives its first answer. For questions that did not receive an answer by the download date, time until event values were defined as the time since posting to the time the data was downloaded. These questions were considered right-censored, meaning that exact answer times for these questions are greater than the recorded times (questions can still receive answers after the download date).

Survival was defined as the event that a question does not receive an answer beyond a certain time, t. Estimates of survival probability were generated with the Kaplan-Meier method (cite). This method adjusts to the presence of right-censored, or unanswered questions. Estimates factor in the number of questions that have not been answered on each ordered interval of complete answer times. The estimates of survival probablity are the products of all probabilities up to that interval's time (fix this explanation). From these estimates, survival curves were constructed to examine the survival experience of questions. Mean, median and other percentiles of survival times were also generated.

As the probability distribution for answer times was unknown, a nonparametric Cox proportional hazards model was developed to predict survival probability (Cox models are not based on an assumption of the shape of the underlying probability distribution). To build the model, five-fold cross-validation was used. The full data was split into five training and five test sets. Each training set contained 6,208 questions, and each test set contained 1,552 questions. Univariate analysis, performed on one of the training sets, was used to identify variables to include in the full Cox proportional hazards model. Predictors were entered into separate Cox models and the strength of association between those predictors and answer times were assessed. Those with partial likelihood ratio test p-values of less than 0.01 were included in the full model.

In each fold of cross-validation, the full model, with variables found to be signficant in univariate analysis, was built on one of the training sets and used to generate predicted hazard ratios on the corresponding test sets. To assess prediction performance, the predicted hazard ratios were entered into separate Cox models as the single quantitative predictor with answer times as the survival time. The resulting estimated hazard ratio, R-square statistic, partial likelihood ratio and p-value were assessed as indicators of the full model's performance \citep{Chen}. Signficant statistics would indicate high predictive accuracy. Concordance statistics and Somers' Dxy were also assessed to measure the model's predictive discrimination. Concordance is defined as the probability that for any two randomly chosen questions, the question with the shorter survival time also has the higher predicted hazard. Concordance statistics close to 1 indicate high discriminative ability, while statistics close to 0.5 indicate discordance, or random predictions. Somers' Dxy is the difference between the model's concordance statistic and discordance (0.5) \citep{Harrell2015}. These metrics were computed for each training and test set. The averages of metrics across test sets were evaluated. The final model was selected based on AIC statistics and signficance of prediction metrics, as well as how consistent those metrics were across training and test sets. The final model was then fit to the full data and the same metrics were computed and compared.

Plots of Martingale residuals, the differences between observed number of answers received by each question and the expected number of answers expereinced by each question under the model, were evaluated to assess functional form of each continuous predictor. Deviance residuals, transformed Martingale residuals with a mean of 0 and approximately normal distribution, were assessed to identify questions poorly predicted by the model. Score residuals, a measure of the approximate change in parameter estimates that would occur if a question were removed from the sample, were assessed to check for questions that highly effect parameter estimates.

As the data analyzed was fairly large, restricted cubic splines were applied to all continuous predictors \citep{Harrell2015}. Splines of five knots were initially fit to each. The optimal number of knots for each predictor was determined based on the model AIC statistic. A higher number of knots were assigned to predictors hypothesized to be more signficant, those with lower model p-values.

Correlations between scaled Schoenfeld residuals, the differences between observed and expected predictor values for each question that received an answer, and a function of time were examined to assess the proportional hazards assumption that underlies a Cox proportional hazards model. Proportional hazards assumes that the effect of predictors on hazard does not depend on time. Significant correlations would indicate that a predictor has violated this assumption.

@@

  Of 7,760 questions, 63.8\% received an answer by the download date. Figure a shows the distribution of answer times for all questions, grouped by whether or not the question received an answer. The following statistics were calculated from Kaplan-Meier estimates of survival probability. The mean survival time, or the average time until a question received its first answer was 775.75 hours, or 32.32 days. The median survival time, the time at which 50\% of the questions in the data received an answer was 9.16 hours. Table 1 provides more percentiles of survival time. Figure B shows the Kaplan-Meier curve for all questions in the data. The curve indicates that at around 100 hours after a question is posted, survival probability remains constant at around 0.35.

Predictors with p-values less than 0.01 in univariate analysis are in table b, and were included in the full Cox model for cross-validation. Average metrics for test and training sets are in table c. Although not impressively high, metrics did not change substantially from training to test set, indicating that the model does not overfit. Restricted cubic splines were fit to continous predictors. Splines of five knots were fit to the average frequency of question's tags as well as to the number of characters in the user-defined device name. Splines of four knots were fit to the number of characters in a question's text, average number of characters in a question's tags, and the ratio of number of line breaks to the number of characters in a question's text. Results of cross-validation for the model including the splines are in table d. As refitting the model without insignificant predictors did not effect predictive performance, all variables were included. The final model, with all variables described above including splines, was fit to the full data.

Score and deviance residuals of the final model identified outliers and highly influential questions. However, because refitting the model without those questions resulted in worse predictive accuracy, all questions were left in the data. Assessing the proportional hazards assumption indicated that several levels of the device category predictor were in violation. But as stratifying on this predictor substantially decreased predictive accuracy, the variable was left as is. Statistics and parameter coefficients of the final model are in table c.
